\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\setlength{\footskip}{4.08003pt}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable when supported
\ifPDFTeX
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge C S Vaishakh} \\ \vspace{1pt}
    \small \href{mailto:vaishakhsubramonian@gmail.com}{\underline{vaishakhsubramonian@gmail.com}} \\ \vspace{1pt}
    \small \href{https://linkedin.com/in/csvaishakh}{\underline{linkedin}} $|$
    \href{https://github.com/CSVaishakh}{\underline{github}} $|$
    \href{https://vaishakh.vercel.app/}{\underline{portfolio}} \\ \vspace{1pt}
    \small +91 7511137620
\end{center}

%-----------ABOUT----------
\section*{Professional Summary}
AI \& Data Science undergraduate student with a strong interest in backend development, systems architecture, and machine learning. Experienced in building RESTful APIs using Go (Fiber) and Node.js (Express), managing relational databases like PostgreSQL, and developing full-stack web applications.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {St. Joseph's College of Engineering and Technology, Palai}{Kottayam, Kerala}
    {B.Tech in Artificial Intelligence and Data Science --- APJ Abdul Kalam Technological University}{2023 -- 2027}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{\href{https://github.com/CSVaishakh/QuickHand}{Quickhand -- Handyman Hiring Platform}}}{December 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Implemented RBAC across 2 user types, securing Fiber API routes and verifying sessions with stateless JWTs.}
        \resumeItem{Designed 2 hiring workflows that cut the booking steps from 7 to 3 for both clients and handymen.}
        \resumeItem{Engineered a high-performance monorepo using a Go backend (Fiber v3) and a React frontend (TanStack Start) orchestrated via Bun.}
        \resumeItem{\textbf{Technologies}: Go, Fiber v3, React, TanStack Start, TypeScript, Tailwind CSS, PostgreSQL, GORM, Docker}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{\href{https://github.com/CSVaishakh/CourseSellingApp}{Course Selling Platform -- Backend System}}}{November 2025}
      \resumeItemListStart
        \resumeItem{Developed a RESTful backend API in Node.js and Express.js (v5) supporting course lifecycle operations across admin and student roles.}
        \resumeItem{Designed database schemas and relationships using MongoDB/Mongoose to track users, courses, and purchased registrations.}
        \resumeItem{Implemented stateless JWT-based authentication and Bcrypt password hashing to secure endpoints and restrict role actions.}
        \resumeItem{\textbf{Technologies}: Node.js, Express.js, MongoDB, Mongoose, JWT, Bcrypt}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{\href{https://github.com/CSVaishakh/ONT-Monitor}{ONT Monitor -- ONT Connection Tracker}}}{April 2026}
      \resumeItemListStart
        \resumeItem{Built a Go-based microservice utilizing Fiber v3 and GORM to ingest and process real-time status change events for ONTs.}
        \resumeItem{Implemented thread-safe in-memory queues and a background worker pool to evaluate outages and prevent data race conditions.}
        \resumeItem{Integrated Twilio API to dispatch automated outage and recovery WhatsApp alerts to registered customers upon state transitions.}
        \resumeItem{\textbf{Technologies}: Go, Fiber v3, GORM, PostgreSQL, Twilio API, Docker}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{\href{https://github.com/CSVaishakh/PortfolioIQ}{PortfolioIQ -- Portfolio Rebalancing Platform}}}{December 2025 -- April 2026}
      \resumeItemListStart
        \resumeItem{Engineered a privacy-preserving portfolio rebalancing platform structured as a monorepo using Turborepo and npm workspaces.}
        \resumeItem{Designed a client-side training pipeline using TensorFlow.js to train local logistic regression models on a 12-dimensional feature vector, eliminating raw data uploads.}
        \resumeItem{Implemented the Federated Averaging (FedAvg) algorithm on the Express.js aggregator to synchronize local updates with a FastAPI scikit-learn model.}
        \resumeItem{\textbf{Technologies}: Next.js, Express.js, FastAPI, TensorFlow.js, Drizzle ORM, PostgreSQL, Python, TypeScript, Turborepo, Docker}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Programming}{: Python, TypeScript, Go, Java, JavaScript} \\
	      \textbf{Web \& Backend}{: Next.js, React, Express.js, Fiber v3, FastAPI, Node.js, TanStack Start, REST APIs} \\
	      \textbf{Databases \& ORMs}{: PostgreSQL, MongoDB, GORM, Drizzle ORM, Mongoose} \\
	      \textbf{AI / ML}{: TensorFlow.js, Feature Engineering, Model Evaluation, Scikit-learn, NumPy, Pandas} \\
	      \textbf{Tools}{: Git, GitHub Actions, Docker, Turborepo, Bun, Postman, Linux, VS Code}
	      }}
\end{itemize}


%-------------------------------------------
\end{document}
